---
title: "Bootstrapped Descriptives"
author: "Erin M. Buchanan"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Seed for random number generation
set.seed(89432289)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, include = FALSE)
library(rio)
library(dplyr)
library(nlme)
library(effectsize)
library(ggplot2)
library(ppcor)
library(MuMIn)
library(papaja)

num_boots <- 1000
```

## Data Source

```{r import-data}
# please note the data is deidentified but timing and course number is accurate
DF <- import("../data/final_evals.csv")

# we will only use courses with at least 15 ratings ... look at the paper that may be reliable (2013)
DF_sample <- DF %>% 
  filter(People >= 15)

# for this pre-reg we will randomly sample 20 percent of instructors 
# random_sample <- sample(unique(DF_sample$instructor_code), 
#                         size = round(length(unique(DF_sample$instructor_code)) * .30),
#                         replace = FALSE)
# 
# DF_sample <- DF_sample %>% 
#   filter(instructor_code %in% random_sample)
```

## Descriptive Statistics

`r nrow(DF_sample)` evaluations included at least 15 student evaluations
for analysis. Table \@ref(tab:table1) portrays the descriptive
statistics for each course level including the total number of
evaluations, unique instructors, unique course numbers, and average
scores for the two rating items. Students additionally projected their
course grade for each class (*A* = 5, *B* = 4, *C* = 3, *D* = 2, *F* =
1), and the average for this item is included for reference. Overall,
`r length(unique(DF_sample$instructor_code))` unique instructors and
`r length(unique(DF_sample$new_course))` unique courses were included in
the analyses below across `r max(DF_sample$semester_count) + 1`
semesters.

```{r table1, results = 'asis', include = TRUE}
save_descriptives <- list()

for (i in 1:num_boots){
  
  DF_boot <- DF_sample %>% 
    slice_sample(n = nrow(DF_sample), replace = TRUE)
  
  save_descriptives[[i]] <- DF_boot %>% 
  group_by(course_level) %>% 
  summarize(totaln = n(), 
            num_instruct = length(unique(instructor_code)),
            num_courses = length(unique(new_course)),
            avg_people = apa_num(mean(People, na.rm = T)), 
            avgq1 = apa_num(mean(Q1AVG, na.rm = T)), 
            avgsd1 = apa_num(sd(Q1AVG, na.rm = T)), 
            avgq4 = apa_num(mean(Q4AVG, na.rm = T)),
            avgsd4 = apa_num(sd(Q4AVG, na.rm = T)),
            avgq15 = apa_num(mean(Q15AVG, na.rm = T)), 
            avgsd15 = apa_num(sd(Q15AVG, na.rm = T))) %>% 
  arrange(desc(course_level))
  
}

temp <- bind_rows(save_descriptives) %>% 
  mutate(course_level = factor(course_level, 
                               levels = c("undergraduate",
                                          "mixed", 
                                          "masters"))) %>% 
  group_by(course_level) %>% 
  mutate(across(totaln:avgsd15, as.numeric)) %>% 
  summarize(across(totaln:avgsd15, mean),
            across(totaln:avgsd15, apa_num)) %>% 
  t() %>% 
  as.data.frame() %>% 
  slice(-1)

temp$stat <- c("N Total", "N Instructors", "N Courses",
               "Average N Ratings", "Average Overall", 
               "SD Overall", "Average Fairness", 
               "SD Fairness", "Average Grade", "SD Grade")
apa_table(temp[ , c(4, 1:3)], 
          caption = "Bootstrapped Descriptive Statistics of Included Courses", 
            row.names = FALSE, 
            col.names = c("Statistic", "Undergraduate", "Mixed", "Master's"))
```

