---
title: "Bootstrapped RQ4"
author: "Erin M. Buchanan"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
# Seed for random number generation
set.seed(89432289)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
library(rio)
library(dplyr)
library(nlme)
library(effectsize)
library(ggplot2)
library(ppcor)
library(MuMIn)
library(papaja)

num_boots <- 1000
```

## Data Source

```{r import-data}
# please note the data is deidentified but timing and course number is accurate
DF <- import("../data/final_evals.csv")

# we will only use courses with at least 15 ratings ... look at the paper that may be reliable (2013)
DF_sample <- DF %>% 
  filter(People >= 15)

# for this pre-reg we will randomly sample 20 percent of instructors 
# random_sample <- sample(unique(DF_sample$instructor_code), 
#                         size = round(length(unique(DF_sample$instructor_code)) * .30),
#                         replace = FALSE)
# 
# DF_sample <- DF_sample %>% 
#   filter(instructor_code %in% random_sample)
```

## RQ 1 Data Set Up

```{r rq1-nlme}
# create matched dataframe
# let's see if twitter can help here - yes! @smartin2018 for the win!

# create unique id
DF_sample$evalid <- 1:nrow(DF_sample)

# create every pairwise combination 
combns <- t(combn(DF_sample$evalid,2))

# create a dataframe to hold that information, remove other frame for the love of space
longrel <- data.frame(evalid=combns[,1],evalid2=combns[,2]); rm(combns)

# add person 1 information back to dataframe
templong <- merge(longrel, DF_sample, by = "evalid")
colnames(templong)[1:2] <- c("evalid1", "evalid")

# add person 2 information back to the dataframe, remove other frame for the love of space
longrel <- merge(templong, DF_sample, by = "evalid")
rm(templong)

# create factors
longrel$instructormatch <- as.numeric(longrel$instructor_code.x == longrel$instructor_code.y)
longrel$semestermatch <- as.numeric(longrel$semester_count.x == longrel$semester_count.y)
longrel$coursematch <- as.numeric(longrel$new_course.x == longrel$new_course.y)
```

## RQ 2 Set Up

```{r rq2-setup, warning = FALSE}
# filter to only matches
long_match <- longrel %>% 
  filter(coursematch == 1) %>% 
  filter(instructormatch == 1) %>% 
  dplyr::select(instructor_code.x, semester_count.x, People.x, Q1AVG.x, Q4AVG.x, 
         instructor_code.y, semester_count.y, People.y, Q1AVG.y, Q4AVG.y) %>% 
  mutate(semester_diff = round(semester_count.y - semester_count.x))

# figure out the number each person has and need at least 10
long_summary <- long_match %>% 
  group_by(instructor_code.x, semester_diff) %>% 
  summarize(total_n = n(), .groups = "keep", 
            avg_fair = mean(c(Q4AVG.x, Q4AVG.y), na.rm = T), 
            std_fair = sd(c(Q4AVG.x, Q4AVG.y), na.rm = T)) %>% 
  filter(total_n >= 10) %>% 
  mutate(code = paste0(instructor_code.x, semester_diff))

long_match$code <- paste0(long_match$instructor_code.x, long_match$semester_diff)

save_rel <- data.frame(
  code = 1:nrow(long_summary), 
  rel = 1:nrow(long_summary)
)

for (i in 1:nrow(long_summary)){
  temp <- long_match %>% 
    filter(code %in% long_summary$code[i]) %>% 
    dplyr::select(Q1AVG.x, Q1AVG.y, People.x, People.y) %>% 
    pcor()
  save_rel$code[i] <- long_summary$code[i]
  save_rel$rel[i] <- temp$estimate[2, 1]
}

save_rel <- save_rel %>% 
  left_join(long_summary %>% dplyr::select(code, instructor_code.x, semester_diff, avg_fair, std_fair) %>% unique(), by = "code")
```

## RQ 4

```{r rq4-nlme}
# center the variables
save_rel$std_fair_center <- scale(save_rel$std_fair, scale = FALSE)
save_rel$std_fair_low <- save_rel$std_fair_center + sd(save_rel$std_fair_center, na.rm = T)
save_rel$std_fair_high <- save_rel$std_fair_center - sd(save_rel$std_fair_center, na.rm = T)
save_rel$avg_fair_center <- scale(save_rel$avg_fair, scale = FALSE)
save_rel$avg_fair_low <- save_rel$avg_fair_center + sd(save_rel$avg_fair_center, na.rm = T)
save_rel$avg_fair_high <- save_rel$avg_fair_center - sd(save_rel$avg_fair_center, na.rm = T)
save_rel$z_semester_diff <- scale(save_rel$semester_diff, scale = FALSE)

save_results <- list()
save_R2 <- list()
save_coef <- list()
save_ciL <- list()
save_ciH <- list()
save_coef2 <- list()
save_ciL2 <- list()
save_ciH2 <- list()

for (i in 1:num_boots){
  
  DF_boot <- save_rel %>% 
    slice_sample(n = nrow(save_rel), replace = TRUE)
    

  save_results[[i]] <- lme(rel ~ z_semester_diff*std_fair_center, 
                 data = DF_boot,
                 random = list(~1|instructor_code.x), 
                 method = "ML", 
                 na.action = "na.omit",
                 control = lmeControl(opt = "optim"))

  save_R2[[i]] <- r.squaredGLMM(save_results[[i]])[1]
  save_coef[[i]] <- summary(save_results[[i]])$tTable[4,1]
  save_ciL[[i]] <- intervals(save_results[[i]])$fixed[4,1]
  save_ciH[[i]] <- intervals(save_results[[i]])$fixed[4,3]
  
  save_coef2[[i]] <- summary(save_results[[i]])$tTable[3,1]
  save_ciL2[[i]] <- intervals(save_results[[i]])$fixed[3,1]
  save_ciH2[[i]] <- intervals(save_results[[i]])$fixed[3,3]

}

R2_boot <- mean(unlist(save_R2))
coef_boot <- mean(unlist(save_coef))
ciL_boot <- mean(unlist(save_ciL))
ciH_boot <- mean(unlist(save_ciH))

coef_boot2 <- mean(unlist(save_coef2))
ciL_boot2 <- mean(unlist(save_ciL2))
ciH_boot2 <- mean(unlist(save_ciH2))
```

The confidence interval for the interaction of variability of fairness and semester time difference did cross zero, *b* =
`r apa_num(coef_boot, digits = 3)`, 95% CI [`r apa_num(ciL_boot, digits = 3)`,
`r apa_num(ciH_boot, digits = 3)`], $R^2$ =
`r suppressWarnings(apa_num(R2_boot, gt1 = FALSE))`. The variability of fairness also did not predict reliability overall, *b* =
`r apa_num(coef_boot2, digits = 3)`, 95% CI [`r apa_num(ciL_boot2, digits = 3)`,
`r apa_num(ciH_boot2, digits = 3)`]. 